### 2022-10-04 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@cfc35072323c390515c168da89a05baaa02a78d6 🚀

\begin{figure}
\hypertarget{fig:embedding}{%
\centering
\includegraphics{figures/conceptual_2.png}
\caption{Overview of the embedding and transfer process. A network
(\textbf{A}), represented here as its adjacency matrix, is converted
into a lower-dimensional object (\textbf{B}) where nodes, subgraphs, or
edges have specific values (see tbl.~\ref{tbl:methods} for an overview
of methods and their use for species interactions). For the purposes of
prediction, this low-dimensional object encodes feature vectors for
\emph{e.g.} the nodes. Embedding also allows to visualize the structure
in the data differently (see fig.~\ref{fig:illustration}), much like
with a principal component analysis. From a low-dimensional feature
vector, it is possible to develop predictive approaches. Nodes in an
ecological network are usually species (\textbf{C}), for which we can
leverage phylogenetic relatedness (\emph{e.g.} Strydom et al., 2022) or
functional traits to fill the values of additional species we would like
to project in this space (here for nodes I, J, K, and L) from the
embedding of known species (here, nodes A, B, C, and D). Because
embeddings can be projected back to a graph, this allows us to
reconstruct a network with these new species (\textbf{D}). This entire
cycle constitutes an instance of transfer learning, where the transfered
information is the representation of graph \textbf{A} through its
embedding.}\label{fig:embedding}
}
\end{figure}

>>>>

\begin{figure}
\hypertarget{fig:embedding}{%
\centering
\includegraphics{figures/conceptual_2.png}
\caption{Overview of the embedding and transfer process. A network
(\textbf{A}), represented here as its adjacency matrix, is converted
into a lower-dimensional object (\textbf{B}) where nodes, subgraphs, or
edges have specific values (see tbl.~\ref{tbl:methods} for an overview
of methods and their use for species interactions). For the purposes of
prediction, this low-dimensional object encodes feature vectors for
\emph{e.g.} the nodes. Embedding also allows to visualize the structure
in the data differently (see fig.~\ref{fig:illustration}), much like
with a principal component analysis. From a low-dimensional feature
vector, it is possible to develop predictive approaches. Nodes in an
ecological network are usually species (\textbf{C}), for which we can
leverage phylogenetic relatedness (\emph{e.g.} Strydom et al., 2022) or
functional traits to fill the values of additional species we would like
to project in this space (here for nodes I, J, K, and L) from the
embedding of known species (here, nodes A, B, C, and D). Because
embeddings can be projected back to a graph, this allows us to
reconstruct a network with these new species (\textbf{D}). This entire
cycle constitutes an instance of transfer learning, where the
transferred information is the representation of graph \textbf{A}
through its embedding.}\label{fig:embedding}
}
\end{figure}
